Growing libraries of concepts with wake-sleep program induction

### 2018-07-31 nips_2018_author_response.tex
a bunch of editing

\begin{SCfigure}[2][h]
  \centering
  \includegraphics[width=7cm]{figures/rebutal/spirals.eps}\label{geomCompiled}
  \caption{Practical example of DSL evolution: originally, the preferred program
  for the leftmost spiral does not use loops while that of the two other does.
  After an iteration the structure of the two rightmost spiral is abstracted.
  For the next iteration the preferred program for the leftmost spiral leverages
  on that and changes in a meaningful way.}
\end{SCfigure}

>>>>

\subsubsection*{The evolution of task solutions over time}
Reviewer 1 asks about the ``evolution of solutions to a fixed task through the iterations of the main algorithm.''
In most cases the solution to a fixed task
stays the same,
modulo rewriting the solution in terms of new subroutines.
There are interesting cases however where the
semantics of the program changes as the algorithms constructs more subroutines. Figure~\cite{geomCompiled}
illustrates one case for turtle graphics.
\begin{SCfigure}[2][h]
  \centering
  \includegraphics[width=7cm]{figures/rebutal/spirals.eps}\label{geomCompiled}
  \caption{Three turtle graphics tasks: the task is to write a program that draws the image. Initially SSC solves the leftmost task without using a loop, but after solving the middle and rightmost tasks,
  it constructs a parametric `spiral' subroutine, which uses a loop -- on subsequent iterations it solves the leftmost task using the `spiral' routine.}
\end{SCfigure}
